\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{5pt}

\urlstyle{same}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{description}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{description}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

% Heading
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Nick Taylor} & \href{mailto:nick@nicktaylor.ca}{nick@nicktaylor.ca}\\
  \href{https://www.nicktaylor.ca/}{https://www.nicktaylor.ca} & Ottawa, Ontario
\end{tabular*}

% Education
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Athabasca University}{Correspondence}
      {Bachelor of Science, Computing and Information Systems}{2016 - Present}
    \resumeSubheading
      {University of Calgary}{Calgary, Alberta}
      {Bachelor of Science, Computer Science}{2014 - 2016}
  \resumeSubHeadingListEnd

% Experience
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shopify}{Ottawa, Ontario}
      {Internal Security Developer}{June 2018 - Present}
      \resumeItemListStart
        \resumeItem{Development}
          {Developed a Ruby on Rails application to handle authentication and authorization of internal systems. Running in-line for all requests handling upwards of 100 000 requests per minute, with a p99 response time of 10ms.}
        \resumeItem{Mentoring \& People Leadership}
          {Developed interns through both the regular intern stream, as well as part of \href{https://www.devdegree.ca/}{Shopify's Dev Degree program}.}
        \resumeItem{Technical Leadership}
          {Subject matter expert for internal and external authentication and authorization systems, led authorization team for the onboarding of regulated industries onto Shopify's platform.}
        \resumeItem{Zero Trust}
          {Developed internal system to support a zero-trust security system for thousands of employees across dozens of countries.}

      \resumeItemListEnd
    \resumeSubSubheading
      {Internal Security Analyst}{October 2017 - May 2018}
      \resumeItemListStart
        \resumeItem{Development}
          {Developed transparency application for employees to understand the data collected by Shopify's enterprise device management solution.}
        \resumeItem{Device Security}
          {Led Device Security initiative to standardize threat models for employee devices and created device tiering model to support BYOD program.}
        \resumeItem{Identity Security}
          {Overhauled an internal meta-identity management system that supported applications for which we did not have SSO support for (e.g. GitHub).}
      \resumeItemListEnd
    \vspace{3pt}
    \resumeSubheading
      {Telus}{Calgary, Alberta}
      {Security Analyst II}{January 2017 - Sep 2017}
      \resumeItemListStart
        \resumeItem{Development}
          {Developed automation systems for incident response, including a machine learning system for classifying and responding to internally-targeted phishing campaigns.}
        \resumeItem{Malware Reverse Engineering}
          {Reverse engineered malware targeted at Telus employees to determine capabilities, source, and target.}
      \resumeItemListEnd
    \resumeSubSubheading
      {Security Analyst I}{June 2015 - December 2016}
      \resumeItemListStart
        \resumeItem{Incident Response}
          {Responded to and managed incidents relating to internal systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% Projects
\section{Projects}
  All projects can be viewed at \href{https://www.nicktaylor.ca/projects}{https://www.nicktaylor.ca/projects}.
  \resumeItemListStart
    \resumeSubItem {Sorting Algorithm Visualization}
      {A visualization tool for different sorting algorithms.}
    \resumeSubItem {Stackless EVEmu}
      {A partial rewrite of the \href{https://github.com/evemuproject/evemu_server}{EVEmu EVE Online server} written in Stackless Python, and based on reverse engineering of the EVE Online client.}
    \resumeSubItem{Trawler}
      {A simple Python Flask application to help ingest and manage phishing reports for SOC teams.}
  \resumeItemListEnd

% Projects
\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Making Technical Decisions}{Ottawa, Ontario}
      {Shopify Summit}{2019}
    \resumeSubheading
      {Automating Malware Analysis}{Calgary, Alberta}
      {BSides Calgary}{2017}
    \resumeSubheading
      {Reverse Engineering MMOs for Questionable Fun and No Profit}{Calgary, Alberta}
      {c0wsec}{2017}
  \resumeSubHeadingListEnd

\end{document}
